The Impact of Educational Expenses of New Coders

### 2021-04-22 outputs/paper/paper.Rmd
Edit continous variables for education level

### Display the result in a table
dfModelValid <-
  data.frame(vecModel, vecRSQ, vecMSE, vecRMSE) %>%
  kable(caption = "Results of model validation metrics",
        booktabs = TRUE,
        col.names = c("Model", "R-squared", "MSE", "RMSE")) %>%
  column_spec(column = 1, width = "4cm") %>%
  column_spec(column = 2:4, width = "3cm")

@@

### Calculate R-squared, MSE, and RMSE for each model
vecModel_city <-
  c("Model (1)", "Model (2)", "Model (3)", "Model (4)")

@@

### Display the result in a table
dfModelValidCity <-
  data.frame(vecModel_city, vecRSQ_city, vecMSE_city, vecRMSE_city) %>%
  kable(caption = "Results of model validation metrics",
        booktabs = TRUE,
        col.names = c("Model", "R-squared", "MSE", "RMSE")) %>%
  column_spec(column = 1, width = "4cm") %>%
  column_spec(column = 2:4, width = "3cm")

>>>>

### Display the result in a table
dfModelValid <-
  data.frame(vecModel, vecRSQ, vecMSE, vecRMSE) %>%
  kable(caption = "Results of model validation metrics for model group 1",
        booktabs = TRUE,
        col.names = c("Model", "R-squared", "MSE", "RMSE")) %>%
  column_spec(column = 1, width = "4cm") %>%
  column_spec(column = 2:4, width = "3cm")

@@

### Calculate R-squared, MSE, and RMSE for each model
vecModel_city <-
  c("Model (4)", "Model (5)", "Model (6)", "Model (7)")

@@

### Display the result in a table
dfModelValidCity <-
  data.frame(vecModel_city, vecRSQ_city, vecMSE_city, vecRMSE_city) %>%
  kable(caption = "Results of model validation metrics for model group 2",
        booktabs = TRUE,
        col.names = c("Model", "R-squared", "MSE", "RMSE")) %>%
  column_spec(column = 1, width = "4cm") %>%
  column_spec(column = 2:4, width = "3cm")
